R Notebook

### 2016-07-27 finalwriteup/trial_code_eq.rmd
abstract

If conditional independence is assumed, the equation becomes:

$p(yes|X_1 X_2) = p(X_1|yes) \cdot p(X_2|yes) \cdot p(yes)$

@@

where $\boldsymbol{w}$ and $\boldsymbol{x}$ are vectors with lengths corresponding to the number of explanatory variables. For two variables, $\boldsymbol{w}$ would be $\begin{pmatrix}\beta_1 \\ \beta_2\end{pmatrix}$ and $\boldsymbol{w}$ would be $\begin{pmatrix}X_1 \\ X_2\end{pmatrix}$. Expanding the dot product of these two vectors gives the equation for a line:

>>>>

@@

where $\boldsymbol{w}$ and $\boldsymbol{x}$ are vectors with lengths corresponding to the number of explanatory variables. For two variables, $\boldsymbol{w}$ would be $\begin{pmatrix}\beta_1 \\ \beta_2\end{pmatrix}$ and $\boldsymbol{w}$ would be $\begin{pmatrix}X_1 \\ X_2\end{pmatrix}$ [@Fletcher2009]. Expanding the dot product of these two vectors gives the equation for a line:
